Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-03-31 paper/src/paper.tex
ccl draft

>>>>

The scheduling of parallel jobs on a given HPC platform is a very hard
optimization problem with many uncertain parameters. Even thought these
uncertainties could be reduced, determining efficient strategies remains
difficult.

We presented in this work a new way of addressing this problem.  The idea was
to look at the level of the scheduling process instead of trying to change its
parameters.

More precisely, we showed that it is worth to learn on the scheduling process
itself. Indeed, reordering the submission queues under EASY-BackFilling leads
to considerable gains in performance.

This approach was used in two methods: a method based on a simulator and a
method based on multi-armed bandits. The first one provides very good results,
improving the average waiting times of the baseline FCFS ordering policy by a
factor of \textcolor{orange}{X} to \textcolor{orange}{X} The second one is
slighly less efficient with an improvement factor of  \textcolor{orange}{X} to
\textcolor{orange}{X}. However, it is more easy to use and less costly to run.

There are two directions for extensions of this work.  First, the question of
the existence of a more efficient selection strategy for bandit feedback for
these systems is not addressed by this work. Is a simulator really necessary?
%@Denis: a essayer.. 1 mois de travail pour tester?
Second, one can help but wonder what performance could be achieved by extending
the search space to arbitrary policies. This means doing a complete study
including lower bounding the cost and studying learning performance using some
function approximator.
%@Denis: c'est ce que font vasily et salah de deux manieres differentes.
As these directions are data-bound, they will require careful application of
trace resampling techniques in order to be successful.
